Wigglyhedra

### 2024-11-15 FPSAC25/wigglyhedraFPSAC.tex
improve last section

For a general object \(X\) of \(\mathcal{C}_m\), the indecomposable factors of the cohomology filtration can be arbitrary.
However, the cohomology filtration is highly constrained if \(X\) is spherical, and these constraints are given by wiggly pseudotriangulations.
This categorical interpretation of the pseudotriangulations was our initial motivation to study the wiggly complex.

>>>>

For a general object \(X\) of \(\mathcal{C}_m\), the indecomposable factors of the cohomology filtration can be arbitrary.
However, the cohomology filtration is highly constrained if \(X\) is spherical, and these constraints are given by wiggly pseudotriangulations (see \cref{prop:wigglyPseudotriangulations}).
This categorical interpretation of the pseudotriangulations was our initial motivation to study the wiggly complex.
